\documentclass{report}
\usepackage{polski}
\usepackage{url}
\usepackage[utf8]{inputenc}
\begin{document}

Inne podejście omówili \cite{Chin1998,Igbaria1997,Ajzen-tpb}. 
Zobacz także pracę~\cite{EdwardsBagozzi2000}.

\begin{thebibliography}{99}
\bibitem{Ajzen-tpb} Ajzen I., \emph{Theory of planned behavior\/},
 bdw, \url{http://www.people.umass.edu/aizen/tpb.html}.
\bibitem{Andruszkiewicz2004}  Andruszkiewicz G., \emph{Analiza
 mikroekonomiczna oprogramowania o~otwartym źródle -- rola
 przedsiębiorstw w~jego rozwoju}, praca magisterska. Szkoła Główna
 Handlowa, Warszawa 2004,
 \url{http://students.mimuw.edu.pl/~ga189376/mgr.pdf}.
\bibitem{Bartamarkiewicz05}  Barta J., Markiewicz R.,
 \emph{Oprogramowanie Open Source w Świetle Prawa. Między 
 Własnością a~Wolnością}, Kraków, Kantor Wydawniczy ZAKAMYCZE 2005.
\bibitem{Bollen89} Bollen, K.~A. \emph{Structural Equations with 
 Latent Variables}, New York, Wiley~1989.
\bibitem{Chin1998}  Chin W.~W., \emph{The partial least squares 
 approach to structural equation modeling\/}, 
 w: Marcoulides, G.~A., (red.), Modern Methods for Business Research, 
 New Jersey, Lawrence Erlbaum~1998, s.~295--336. 
\bibitem{EdwardsBagozzi2000} Edwards J.~R. i Bagozzi R.~P.,
 On the nature and direction of the relationship between constructs 
 and measures. \emph{Psychological Methods\/} 2000, 5(2), s.~155--174.
\bibitem{Goldberger1975} Goldberger A., \emph{Teoria Ekonometrii\/}, 
 Wyd.~2, Warszawa, PWE 1975.
\bibitem{Igbaria1997}
 Igbaria~M., Zinatelli~N., Cragg~P., Cavaye~A.L.M.,
 Personal computing acceptance factors in small firms: A structural
 equation model, \emph{MIS Quarterly}, 1997, 21(3), s.~279--305.
\bibitem{Sudola2003}
\emph{Marketingowe testowanie produktów}, Sudola~S., Szymczak~J., 
 Haffer~M. (red.), Warszawa, PWE 2003.
\bibitem{Podrecki2007}  \emph{Prawo internetu\/}, Podrecki~P. (red.), 
 Warszawa, LexisNexis 2007
\end{thebibliography}

\end{document}
